Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-09 latex-acm/cloneoverflow.tex
Latest updates
Updated the table of configurations

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 84 clones that have been obviously copied from open source projects to Stack Overflow as code examples which potentially violate their software licenses. Furthermore, 50 out of the 84 clones are outdated and questionable for being reused.

@@

In the manual inspection process, we classify clones into categories according to their properties. This process takes approximately a months until we successfully classified 7,840 clone pairs into categories. Some of the clone candidates are false clones due to being boiler-plate code or IDE-generated and are discarded for further analysis. By ignoring the false clones, we compare licensing information of x,xxx remaining clone pairs for possibility of software licensing violations. Moreover, we look forward through history of the clones from the projects' git versioning systems. This is to see if there is any changes made to the clones after it has been copied, hence resulting in outdated clones on Stack Overflow.

@@

%good and ok-match clone pairs are defined as follows. 
A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).  We can define \textit{overlap} and \textit{contained} value of two clone pairs as 
%\squeezeup
\begin{multline}
	overlap(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1) \cup lines(CF_2)|} 
\end{multline}
%\squeezeup
\begin{multline}
	contained(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1)|}. 
\end{multline}

\textit{good-value} of two clone pairs is then defined as
%\squeezeup
\begin{align*}
	good(CP_1, CP_2) = min(overlap(CP_1.CF_1,CP_2.CF_1), \\ overlap(CP_1.CF_2,CP_2.CF_2)).
\end{align*}

Furthermore, \textit{ok-value} is defined as
%\squeezeup
\begin{align*}
	ok(CP_1,CP_2) = min(max(contained(CP_1.CF_1,CP_2.CF_1), \\ contained(CP_2.CF_1,CP_1.CF_1)),
	\\ max(contained(CP_1.CF_2,CP_2.CF_2), \\contained(CP_2.CF_2,CP_1.CF_2))).
\end{align*}

Two clone pairs $CP_1$ and $CP_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(CP_1,CP_2) \geq p.
\end{equation}

Similarly for an \textit{ok-match(p)} pair
%\squeezeup
\begin{equation}
ok(CP_1,CP_2) \geq p.
\end{equation}

@@

\subsection{Clone detectors' parameter tuning}
We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 of Simian's and 5 of NiCad's parameters, we are hindered from finding the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.

\section{Results}
The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements. The average percentage of code in Stack Overflow snippets that are clones reported by Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\% and 21\% accordingly.

\begin{table}[H]
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
		\hline
		\textit{Successful} & 109 & 109 & 97 & 82 \\ 
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

\begin{table*}[h]
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
	\label{tab:raw_stats}
%	\resizebox{\columnwidth}{!}{%
	\small
		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
			\hline
			\multirow{3}{*}{Statistics} 
			& \multicolumn{3}{c|}{Simian$_{df}$} 
			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
			& \multicolumn{3}{c|}{NiCad$_{df}$} 
			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
			& \multicolumn{3}{c|}{1406 fragments} 
			& \multicolumn{3}{c|}{1360 fragments}  
			& \multicolumn{3}{c|}{1197 fragments} 
			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
			\hline
			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
			\hline
		\end{tabular} %
%	}
\end{table*}

@@

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs)}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
		\hline 
		\hline 
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 319 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
			%		\hline
	\end{tabular} 
	}
\end{table*}

@@

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 33 & 8 & 49 \\
%		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
%		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
		Simian$_{df}$ pairs & 71 & 0 & 318 & 10 & 399 \\
%		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
%		NiCad$_{df}$ pairs-2 & 0 & 0 & 10 & 0 & 10 \\
		NiCad$_{df}$ pairs & 4 & 0 & 15 & 0 & 19 \\
		\hline 
		Total & 84 & 0 & 370 & 21 & 475 \\
		\hline
	\end{tabular} 
\end{table}

>>>>

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 238 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses. Furthermore, 50 out of the 84 clones are outdated and questionable for being reused.

@@

In the manual inspection process, we classify clones into categories according to their properties. This process takes approximately a months until we successfully classified 7,840 clone pairs into categories. Some of the clone candidates are false clones due to being boiler-plate code or IDE-generated and are discarded for further analysis. By ignoring the false clones, we compare licensing information of 477 remaining clone pairs for possibility of software licensing violations. Moreover, we look forward through history of the clones from the projects' git versioning systems. This is to see if there is any changes made to the clones after it has been copied, hence resulting in outdated clones on Stack Overflow.

@@

%good and ok-match clone pairs are defined as follows. 
A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).  We can define \textit{overlap} and \textit{contained} value of two clone pairs as 
%\squeezeup
\begin{multline}
	overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{multline}
%\squeezeup
\begin{multline}
	contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}. 
\end{multline}

\textit{good-value} of two clone pairs is then defined as
%\squeezeup
\begin{align*}
	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2)).
\end{align*}

Furthermore, \textit{ok-value} is defined as
%\squeezeup
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2), \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2))).
\end{align*}

Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
%\squeezeup
\begin{equation}
good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

Similarly for an \textit{ok-match(p)} pair
%\squeezeup
\begin{equation}
ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
\end{equation}

@@

\subsection{Clone detectors' parameter tuning}
We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 of Simian's and 5 of NiCad's parameters, we are hindered from finding the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
	\resizebox{\columnwidth}{!}{%
		\scriptsize
\begin{tabular}{l|p{5.5cm}}
	\hline 
	Tool & Parameters \\
	\hline
	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
	\hline
	Simian$_{\textrm{\textit{EvCl}}}$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
	\hline 
	NiCad$_{\textrm{\textit{df}}}$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
	\hline
	NiCad$_{\textrm{\textit{EvCl}}}$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
	\hline 
\end{tabular} %
}
\end{table}

\section{Results}

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
			\hline
			Snippets & 1,406 & 1,360 & 1,197 & 12,884 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 54,790 & 59,936,722 & 127,305 & 206,718,663 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 52 & 44,104 & 106 & 16,046 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.45 & 4.81 & 9.54 & 5.31 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 28\% & 29\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements. The average percentage of code in Stack Overflow snippets that are clones reported by Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\% and 21\% accordingly.

\begin{table}
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
		\hline
		\textit{Successful} & 109 & 109 & 97 & 82 \\ 
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
	\end{tabular}
\end{table}

%\begin{table*}[h]
%	\centering
%	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
%	\label{tab:raw_stats}
%%	\resizebox{\columnwidth}{!}{%
%	\small
%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
%			\hline
%			\multirow{3}{*}{Statistics} 
%			& \multicolumn{3}{c|}{Simian$_{df}$} 
%			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
%			& \multicolumn{3}{c|}{NiCad$_{df}$} 
%			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
%			& \multicolumn{3}{c|}{1406 fragments} 
%			& \multicolumn{3}{c|}{1360 fragments}  
%			& \multicolumn{3}{c|}{1197 fragments} 
%			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
%			\hline
%			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
%			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
%			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
%			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
%			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
%			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
%			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
%			\hline
%		\end{tabular} %
%%	}
%\end{table*}

@@

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs)}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
		\hline 
		\hline 
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 318 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
			%		\hline
	\end{tabular} 
	}
\end{table*}

@@

%\subsection{Summary of true online clone pairs}
\begin{table}[H]
	\centering
	\caption{Numbers of true positive online clone pairs found by manual investigation}
	\label{tab:classification_true_pairs_summary}
	\small
	\begin{tabular}{l|r|r|r|r|r}
		\hline 
		Tool & A & A' & B & C & Total \\
		\hline
		good-pairs & 1 & 0 & 4 & 3 & 8 \\
		ok-pairs & 8 & 0 & 33 & 8 & 49 \\
%		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
%		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
		Simian$_{df}$ pairs & 71 & 0 & 318 & 10 & 399 \\
%		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
%		NiCad$_{df}$ pairs-2 & 0 & 0 & 10 & 0 & 10 \\
		NiCad$_{df}$ pairs & 4 & 0 & 15 & 0 & 19 \\
		\hline 
		Total & 84 & 0 & 370 & 21 & 476 \\
		\hline
	\end{tabular} 
\end{table}
